---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# forestmodel

This is an R package to generate forest plots of the coefficients of models produced
by `lm`, `glm`, `survival::coxph`, etc.

The main function is `forest_model`, with a helper function `default_forest_panels` to produce
the necessary `panels` `data.frame`.

## Example

```{r example, message = FALSE, fig.keep = "none"}
library("forestmodel")
library("survival")
library("dplyr")
pretty_lung <- lung %>%
  transmute(time,
            status,
            Age = age,
            Sex = factor(sex, labels = c("Male", "Female")),
            ECOG = factor(lung$ph.ecog),
            `Meal Cal` = meal.cal)

print(forest_model(coxph(Surv(time, status) ~ ., pretty_lung)))
```

## Installation

The package can be installed using `install.packages`. It needs Hadley Wickham's
`broom`, `dplyr`, `gpplot2` and `lazyeval` packages.

[![Build Status](https://travis-ci.org/NikNakk/forestmodel.svg?branch=master)](https://travis-ci.org/NikNakk/forestmodel)
